Parameter estimation

### 2023-06-21 SFE-article/Sections/Saturation.tex
21.06

	\subsubsection{Saturation Concentration}

	The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}). $\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$. The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.

	{\footnotesize
		\begin{equation}
			\gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
			\label{EQ: C_sat_function}
			\end{equation}
	}

	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.

@@

				\begin{axis}[
					legend style={draw=none},
					xmin = 0, xmax = 10,
					ymin = -0.5, ymax = 1.5,
					xlabel = {$c_f[kg/m^3]$},
					ylabel = {$\gamma(c_f)[-]$}]
					\addplot[
					domain = 0:10,
					samples = 100,
					smooth,
					thick,
					blue,
					] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};

					\addlegendentry{$\gamma(c_f)$}
					\addlegendentry{$c_{sat}$}
				\end{axis}

			\end{tikzpicture}
			\caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
			\label{fig: Gamma_function}
	\end{figure}

@@

	{\footnotesize
		\begin{equation}
			\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
		\end{equation} }

>>>>

	\subsubsection{Concentration limit}

	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil. The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{magenta} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{magenta} c_{lim}}$. The ${\color{orange} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient. As the concentration of solute decrease, it can reach the limiting value ${\color{magenta} c_{lim}}$ when the ${\color{orange} \gamma}$ goes to zero and stop the extraction from the solid.

	{\footnotesize
		\begin{equation}
			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{magenta} k_{lim}} \left( {\color{blue} c_s} (t,z) - {\color{magenta} c_{lim}} \right) \right) }
			\label{EQ: C_sat_function}
			\end{equation}
	}

	where ${\color{magenta} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{magenta} k_{lim}} = 1$. %In the limit when $ {\color{magenta} k_{lim}}\rightarrow+\infty$ become a step function. If the ${\color{magenta} k_{lim}}$ is to high, the gradient of the ${\color{orange} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer. 
	The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.

@@

				\begin{axis}[
					legend style={draw=none},
					xmin = 0, xmax = 100,
					ymin = -0.5, ymax = 1.5,
					xlabel = {${\color{blue} c_s}(t,z)[kg/m^3]$},
					ylabel = {${\color{orange} \gamma}({\color{blue} c_s}(t,z))[-]$}]
					\addplot[
					domain = 0:100,
					samples = 100,
					smooth,
					thick,
					blue,
					] { 1 / (1 + exp( 1 * ( 50 - x ) ) ) };
					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(50,-0.5)(50,1.5)};

					\addlegendentry{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$}
					\addlegendentry{${\color{magenta} c_{lim}}$}
				\end{axis}

			\end{tikzpicture}
			\caption{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ function under assumption of ${\color{magenta} c_{lim}}=50~[kg/m^3]$}
			\label{fig: Gamma_function}
	\end{figure}

@@

	{\scriptsize
		\begin{equation}
			\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
		\end{equation} }

### 2023-06-21 SFE-article/Sections/Thermodynamic_details.tex
21.06

	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}$ denotes its compressibility factor, and $R$ is the universal gas constant. The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure. It can be written as a cubic function of the molar volume (of the density). Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}. The P-R EOS is presented by Equation \ref{EQ: PR}.

@@

	The Equation \ref{EQ: PR} can be also written as the third-order polynomial equation shown in Equation \ref{eq: Compressibility}. Numerical methods such as Newton-Raphson can be used to solve the polynomial equation, but the Cardano formula is preferred as it yields an analytical solution. Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.

	{\footnotesize	
	\begin{align}\label{eq: Compressibility}
		&{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 \\ \nonumber
		&+ \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0
	\end{align} }

	where ${\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left[{\color{blue}T}(t,z)\right] = {\color{magenta}a^c}{\color{orange}\alpha}\left[{\color{blue}T}(t,z)\right]$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T^c}^2}/{{\color{magenta}P^c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T^c}}/{{\color{magenta}P^c}}$, both functions of the critical temperature ${\color{magenta}T^c}$ and pressure ${\color{magenta}P^c}$.

	{\footnotesize
	\begin{subequations} \label{eq: PR_AB}
		\begin{align} 
			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]{\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
		\end{align}
	\end{subequations}}

	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$. The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.

%	Using the physical constants $\varphi_{Z} = \left(R,T^c_{CO_2},P^c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right]$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.

@@

	The density of the fluid phase, denoted by $\rho_{\text{F}}$, is assumed to be equal to the density of the solvent at a given temperature and pressure. Since the temperature $T(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time. Using an equation of state in the form of ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, the following expression for the density can be obtained:

	{\footnotesize
		\begin{equation} \label{eq: Density}
			{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi{Z}\right]},
	\end{equation}}

	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq. \eqref{eq: Compressibility}. This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T^c{CO_2}}, {\color{magenta}P^c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.

@@

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}. The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are presented below:

	{\footnotesize
	\begin{subequations}\begin{align}
			{\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = {\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] + {\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] \label{eq: Cv_CO2}; \\ 
			{\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = \underbrace{{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right]}_{\text{Eq. } \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq. } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
	\end{align}\end{subequations} }

	${\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $CO_2$ at constant volume and pressure, respectively. ${\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure. ${\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms. \\

	For $CO_2$, the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$ is given by,

	{\footnotesize
	\begin{equation}
		{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
	\end{equation} }

	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$. For the correction term ${\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z){\color{red}P}(t)\right]$ at constant pressure $P(t)$, we have

	{\footnotesize	
	\begin{align}
		&{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] = \underbrace{{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq. }\eqref{eq: CvR}} \nonumber \\
		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}}_{\text{Eq. } \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq. } \eqref{eq: dVdT}} - {\color{magenta}R}. \label{eq: Cp_R} 
	\end{align} }

	The braced terms are obtained from the chosen equation of state $P(t) V\left[T(t,z),P(t)\right] = Z\left[T(t,z),P(t)\right] R T(t,z)$. \\

@@

	{\footnotesize
	\begin{align}
		\left( \cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq. }\eqref{eq: dZdT}} \label{eq: dVdT}
	\end{align} }

	with partial derivative of the compressibility factor with respect to temperature $T$ at constant pressure $P(t)$

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
	\end{equation} }

@@

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}v_m}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
	\end{equation} }

@@

	{\footnotesize
	\begin{equation}
		{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}. \label{eq: CvR}
	\end{equation} }

	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T^c}, {\color{magenta}P^c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.

@@

	{\footnotesize
		\begin{equation}
			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left[T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right]{\frac{dv_m}{v_m}} + 1-Z
		\end{equation}
	}

@@

	{\footnotesize
		\begin{equation}
			h-h^{\mathrm {id} }=RT\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
		\end{equation}
	}

>>>>

	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ denotes its compressibility factor, and $R$ is the universal gas constant. The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure. It can be written as a cubic function of the molar volume (of the density). Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}. The P-R EOS is presented by Equation \ref{EQ: PR}.

@@

	The Equation \ref{EQ: PR} can be also written as the third-order given by Equation \ref{eq: Compressibility}. Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ at given temperature and pressure. Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{eq: Compressibility}. Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.

	{\footnotesize	
	\begin{equation}\label{eq: Compressibility}
	\begin{aligned}
		&{\color{orange}Z}^3 - \left(1 - {\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\right) {\color{orange}Z}^2 \\
		&+ \left({\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 2{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 3{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)^2\right) {\color{orange}Z} = 0
	\end{aligned} \end{equation} }

	where ${\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left({\color{blue}T}(t,z)\right) = {\color{magenta}a^c}{\color{orange}\alpha}\left({\color{blue}T}(t,z)\right)$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T_c}^2}/{{\color{magenta}P_c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T_c}}/{{\color{magenta}P_c}}$, both functions of the critical temperature ${\color{magenta}T_c}$ and pressure ${\color{magenta}P_c}$.

	{\footnotesize
	\begin{subequations} \label{eq: PR_AB}
		\begin{align} 
			{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right){\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
			{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
		\end{align}
	\end{subequations}}

	The quantity ${\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right)$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$. The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.

%	Using the physical constants $\varphi_{Z} = \left(R,T_c_{CO_2},P_c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left({\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right)$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.

@@

	The density of the fluid phase, denoted by ${\color{orange}\rho_f}$, is assumed to be equal to the density of the solvent at a given temperature and pressure. Since the temperature ${\color{blue}T}(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time. Using the definition of compressibility, the following expression for the density can be obtained:

	{\footnotesize
		\begin{equation} \label{eq: Density}
			{\color{orange}\rho_f} \left({\color{blue}T}(t,z),{\color{red}P}(t) \right) = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}Z}\left({\color{blue}T}(t,z),{\color{red}P}(t) \right)},
	\end{equation}}

	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ is the compressibility factor that solves Eq. \eqref{eq: Compressibility}. This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T_c{CO_2}}, {\color{magenta}P_c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.

@@

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}. The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are presented below:

	{\footnotesize
	\begin{subequations}\begin{align}
			{\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = {\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) + {\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) \label{eq: Cv_CO2}; \\ 
			{\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = \underbrace{{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right)}_{\text{Eq. } \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq. } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
	\end{align}\end{subequations} }

	${\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively. ${\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure. ${\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms. \\

	For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{red}P}(t)$, as function of ${\color{blue}T}(t,z)$ is given by,

	{\footnotesize
	\begin{equation}
		{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
	\end{equation} }

	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$. For the correction term ${\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$ at constant pressure ${\color{red}P}(t)$, we have

	{\footnotesize	
	\begin{align}
		&{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) = \underbrace{{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq. }\eqref{eq: CvR}} \nonumber \\
		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}}_{\text{Eq. } \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq. } \eqref{eq: dVdT}} - {\color{magenta}R}. \label{eq: Cp_R} 
	\end{align} }

%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$. \\

@@

	{\footnotesize
	\begin{align}
		\left( \cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq. }\eqref{eq: dZdT}} \label{eq: dVdT}
	\end{align} }

	with partial derivative of the compressibility factor with respect to temperature ${\color{blue}T}$ at constant pressure ${\color{blue}P}(t)$

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
	\end{equation} }

@@

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
	\end{equation} }

@@

	{\footnotesize
	\begin{equation}
		{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right) = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}. \label{eq: CvR}
	\end{equation} }

	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T_c}, {\color{magenta}P_c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left(T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right)$ of the specific heat of the fluid phase.

@@

	{\footnotesize
		\begin{equation}
			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
		\end{equation}
	}

@@

	{\footnotesize
		\begin{equation}
			h-h^{\mathrm {id} }=RT\left(T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right)
		\end{equation}
	}
